A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
References upgrade

Like nature, we identified what most species have in common in the life cycle.
Our algorithm works on a constantly evolving population, experiencing the
stages that all living beings undergo: being born, growing up, reproducing, and
dying, where each of these stages will be processes (of our algorithm) that
randomly affect the population individuals, emulating the organic way.

@@

In this paper, we present an algorithm inspired by the biological Life-Cycle of
animal species, which consists of several stages: birth, growth, reproduction,
and death. As in nature, we intend to execute all these stages in parallel and
asynchronously on a population that evolves constantly.

@@

As a proof-of-concept, we implemented the algorithm with Docker containers by
solving the OneMax problem to compare it with a traditional GA algorithm using
the DEAP (Distributed Evolutionary Algorithms in Python) library. The OneMax
problem uses a genetic algorithm to evolve a population of randomly generated
individuals with zeros and ones, and it stops until a solution of only ones is
found.

@@

We must acknowledge the performance time of the DEAP library is highly
efficient and short, due in part because the processing work execution is on a
single processor with multiple cores, where the communication time is nearly
non-existent. In contrast, our algorithm implementation requires a minimum of
five containers and a message queue server. Even though the container work has
proven to be very effective and efficient [X], we must consider some time was
added to our experiments by the minimal delays (in the thousands of a second
magnitude) we used to keep the process execution relatively random, to mimic
how the life-cycle stages work in nature. As future work, we could test the
Life-Cycle algorithm behavior by eliminating all remaining delays.

@@

We implemented the algorithm with Docker containers by solving the OneMax
problem comparing it with a traditional (sequential) GA algorithm, where it
showed favorable and promising results. To further validate this work, we could
use control or some more complex and demanding problem that requires computing
real numbers.

>>>>

Like nature, we identified what most species have in common in the life cycle.
Our algorithm works on a constantly evolving population, experiencing the
stages that all living beings undergo \cite{read1968system}: being born, growing up, reproducing, and
dying, where each of these stages will be processes (of our algorithm) that
randomly affect the population individuals, emulating the organic way.

@@

In this paper, we present an algorithm inspired by the biological Life-Cycle of
animal species, which consists of several stages \cite{read1968system}: birth, growth, reproduction,
and death. As in nature, we intend to execute all these stages in parallel and
asynchronously on a population that evolves constantly.

@@

As a proof-of-concept, we implemented the algorithm with Docker containers by
solving the OneMax problem to compare it with a traditional GA algorithm using
the DEAP (Distributed Evolutionary Algorithms in Python) library
\cite{fortin2012deap}. The OneMax problem \cite{krejca2020lower,witt2019upper}
uses a genetic algorithm to evolve a population of randomly generated
individuals with zeros and ones, and it stops until a solution of only ones is
found.

@@

We must acknowledge the performance time of the DEAP library
\cite{fortin2012deap} is highly efficient and short, due in part because the
processing work execution is on a single processor with multiple cores, where
the communication time is nearly non-existent. In contrast, our algorithm
implementation requires a minimum of five containers and a message queue
server. Even though the container work has proven to be very effective and
efficient [X], we must consider some time was added to our experiments by the
minimal delays (in the thousands of a second magnitude) we used to keep the
process execution relatively random, to mimic how the life-cycle stages work in
nature \cite{read1968system}. As future work, we could test the Life-Cycle
algorithm behavior by eliminating all remaining delays.

@@

We implemented the algorithm with Docker containers by solving the OneMax
problem comparing it with a traditional (sequential) GA algorithm, where it
showed favorable and promising results. To further validate this work, we could
use control or some more complex and demanding problem that requires computing
real numbers \cite{stanley2002evolving,miikkulainen2019evolving}.
